A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2024-01-05 main.tex
change boilerplate

>>>>

\vspace*{1em}
\paragraph{Note.}
This version of the article has been accepted for publication, after peer
review (when applicable) but is not the Version of Record and does not reflect post-acceptance
improvements, or any corrections. The Version of Record is available online at:
\url{https://doi.org/10.1007/s10664-023-10437-1}. Use of this Accepted Version is subject to the publisher’s Accepted
Manuscript terms of use https://www.springernature.com/gp/open-research/policies/accepted-
manuscript-terms.

To our knowledge, the publisher has not contributed any post-acceptance improvements or corrections, aside from some edits that we reverted.
